Cover letter for the original IJRR submission

### 2017-09-28 body/intro.tex
ongoing, added TODO / DONE macros in letter

\noindent \textbf{Comparison with our previous work:}
The present paper is an extension of our conference paper~\cite{tonneauisrr15}. As such, the motion planning algorithm presented here is the same as the one presented in the
previous work. Section~\ref{rbprm} and~\ref{sec:contact} of the present paper are thus paraphrasing the original paper. However, we provide the pseudo-code of the algorithm,
absent from the original paper. We also improve the computational performance of the method by replacing the static equilibrium test with a more efficient test based on an new LP formulation.
Compared with the original paper, we also release our source code, and provide the complete procedure to use our planner for any legged robot. We thus provide
all the technical information required to use the planner.

>>>>

\noindent \textbf{Comparison with our previous work:}
The present paper is an extension of our conference paper~\cite{tonneauisrr15}. As such, the motion planning algorithm presented here is the same as the one presented in the
previous work. Section~\ref{rbprm} and~\ref{sec:contact} of the present paper are thus paraphrasing the original paper, with the exception of Section~\ref{app:contact}, where we additionally provide the pseudo-code of the algorithm absent from the original paper. We also improve the computational performance of the method by replacing the static equilibrium test with a more efficient test based on an new LP formulation presented in Section~\ref{sec:Equil}..
Compared with the original paper, we also release our source code, and provide the complete procedure to use our planner for any legged robot. We thus provide
all the technical information required to use the planner.

### 2017-09-28 body/results.tex
ongoing, added TODO / DONE macros in letter

These scenarios complement the ones demonstrated on virtual avatars (Figure~\ref{fig:robots_old}) in our previous ISRR paper~\citep{tonneauisrr15} and video\footnote{\url{http://youtu.be/LmLAHgGQJGA}}.
%~ (Figure~\ref{fig:robots_old}).
 %~ We invite the interested reader to watch the ISRR video (\url{http://youtu.be/LmLAHgGQJGA}), and 
%~ to refer to the previous paper for a discussion on these results.

@@

\begin{figure}[t]
\centering
  \begin{overpic}[width=1\linewidth]{figures/robots_old}
		%~ \put (5,) {1)} 
		%~ \put (37,) {2)} 
		%~ \put (68,) {3.a)} 
		%~ \put (5,27) {3.b)} 
		%~ \put (37,27) {4.a)} 
		%~ \put (68,27) {4.b)} 
	\end{overpic}
\caption{Virtual avatars in various scenarios demonstrated in our conference paper.}
		   \label{fig:robots_old}
\end{figure}

@@

\subsubsection{3-fingered hand -- Manipulation of a pen (Figure~\ref{fig:penrot})}
This scenario is proposed to illustrate the generality of our approach: we consider a manipulation task for a robotic hand and use
our contact planner to compute a contact sequence for the fingers, considered as effectors (Figure~\ref{fig:penrot}).
Although we do not address the hard issue of accounting for rolling motions, the planner is able to compute the shown sequences in less than 5 seconds.

\begin{figure*}
\centering
  \begin{overpic}[width=1\linewidth]{figures/penrot}
	\end{overpic}
\caption{Contact sequence found for a pen manipulation in a zero gravity environment.}
		   \label{fig:penrot}
\end{figure*}

\noindent\textbf{Contacts involved:} Three finger-tips.

\noindent\textbf{Heuristics:} $h_{\textrm{\it EFORT}}$ for all fingers.

@@

\subsubsection{Choosing the scaling factor $s$} \label{sec:params}
%~ \deladp{To find a convenient value $s^*$ of $s$, we proceeded as follows. }
For several values of $s$, we generated $10 000$ configurations. 
We then computed the sensitivity of the reachability condition (percentage of configurations in $C_{Reach}^0$, effectively belonging to \gls{$C_{Contact}^0$}).
Similarly we computed the specificity of the condition (percentage of configurations \textbf{not} in $C_{Reach}^0$, effectively \textbf{not} belonging to \gls{$C_{Contact}^0$}).
The obtained results for HRP-2 are shown in Table~\ref{tab:scale}, averaged over all scenes (except for the car egress: in this scenario, 
statistical tests are not really conclusive since we are only interested in a small area of the environment).

>>>>

%~ These scenarios complement the ones demonstrated on virtual avatars (Figure~\ref{fig:robots_old}) in our previous ISRR paper~\citep{tonneauisrr15} and video\footnote{\url{http://youtu.be/LmLAHgGQJGA}}.
%~ (Figure~\ref{fig:robots_old}).
 %~ We invite the interested reader to watch the ISRR video (\url{http://youtu.be/LmLAHgGQJGA}), and 
%~ to refer to the previous paper for a discussion on these results.

@@

%~ \begin{figure}[t]
%~ \centering
  %~ \begin{overpic}[width=1\linewidth]{figures/robots_old}
	%~ \end{overpic}
%~ \caption{Virtual avatars in various scenarios demonstrated in our conference paper.}
		   %~ \label{fig:robots_old}
%~ \end{figure}

@@

%~ \subsubsection{3-fingered hand -- Manipulation of a pen (Figure~\ref{fig:penrot})}
%~ This scenario is proposed to illustrate the generality of our approach: we consider a manipulation task for a robotic hand and use
%~ our contact planner to compute a contact sequence for the fingers, considered as effectors (Figure~\ref{fig:penrot}).
%~ Although we do not address the hard issue of accounting for rolling motions, the planner is able to compute the shown sequences in less than 5 seconds.
%~ 
%~ \begin{figure*}
%~ \centering
  %~ \begin{overpic}[width=1\linewidth]{figures/penrot}
	%~ \end{overpic}
%~ \caption{Contact sequence found for a pen manipulation in a zero gravity environment.}
		   %~ \label{fig:penrot}
%~ \end{figure*}
%~ 
 %~ 
%~ \noindent\textbf{Contacts involved:} Three finger-tips.
%~ 
%~ \noindent\textbf{Heuristics:} $h_{\textrm{\it EFORT}}$ for all fingers.

@@

\subsubsection{Choosing the scaling factor $s$} \label{sec:params}
%~ \deladp{To find a convenient value $s^*$ of $s$, we proceeded as follows. }
For several values of $s$, we generated $10 000$ configurations. 
%~ We then computed the sensitivity of the reachability condition (percentage of configurations in $C_{Reach}^0$ belonging to \gls{$C_{Contact}^0$}).
%~ Similarly we computed the specificity of the condition (percentage of configurations \textbf{not} in $C_{Reach}^0$ \textbf{not} belonging to \gls{$C_{Contact}^0$}).
We then computed to sensitivity and specificity of the reachability condition.  In this context, the sensitivity refers to the percentage of configurations in $C_{Reach}^0$, effectively belonging to \gls{$C_{Contact}^0$}. If a sampled configuration is in $C_{Reach}^0$, but our method is unable to generate a contact configuration from it, as a result the sensitivity
decreases. The sensitivity thus illustrates the confidence we have that any configuration in $C_{Reach}^0$ will effectively lead to a contact configuration.
Conversely, the specificity refers to the percentage of configurations \textbf{not} in $C_{Reach}^0$, effectively \textbf{not} belonging to \gls{$C_{Contact}^0$}.
If a sampled configuration is \textbf{not} in $C_{Reach}^0$, but our method is able to generate a contact configuration from it, as a result the specificity
decreases. The specificity thus illustrates the confidence we have that all configurations that allow contact creation belong to in $C_{Reach}^0$ (or informally, the confidence that we are not missing too many valid solutions).
We thus look for a compromise between sensitivity and specificity.

The obtained results for HRP-2 are shown in Table~\ref{tab:scale}, averaged over all scenes (except for the car egress: in this scenario, 
statistical tests are not really conclusive since we are only interested in a small area of the environment).
